Self recovering capabilities in images using the BPCS Steganography algorithm

### 2014-10-12 Paper/main.tex
Abstract

\noindent Abstract of this dissertation and what I wrote in it.
This will give the reader a short overview of what they can expect to find in this dissertation.

>>>>

\noindent 
Many current self-recovering image methods exist, however few of the current methods provide good quality images after embedding as well as after reconstruction.
This is due to an inherent trade off between the amount of information that can be embedded into an image and the quality of the image after embedding.
This dissertation proposes a novel method for increasing the quality of the image after embedding as well as the quality of the image after reconstruction in the self-recovering image problem using the BPCS Steganography algorithm for content embedding as well as employing a fragile watermark for detecting image modifications.
The proposed method achieves a good quality image after embedding as well as a good quality image after reconstruction when compared with some of the best currently available self-recovering image methods.
